First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-01-19 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
more writing in the coherent prl paper

\documentclass[nofootinbib,twocolumn,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\usepackage{graphicx}
\usepackage{hyperref}
%
\def\Dirac#1{#1\hskip-5pt/}
%
\begin{document}

@@

A wealth of information on the quantum chromodynamics (QCD) structure of hadrons lies in the correlations between the momentum and spatial degrees of freedom of the constituent partons. Such correlations are accessible via the generalized parton distributions (GPDs). The GPDs correspond to the coherence between quantum states of different (or same) helicity, longitudinal momentum, and transverse position. In an impact parameter space, they can be interpreted as a distribution in the transverse plane of partons carrying a certain longitudinal momentum \cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}. A crucial feature of GPDs is the access to the transverse position of partons which, combined with their longitudinal momentum, leads to the total angular momentum of partons \cite{Burkardt:2005hp}. Deep virtual Compton scattering (DVCS) corresponding to hard exclusive electroproduction of a real photon, is considered the cleanest probes to access GPDs and thus study the 3D imaging of nucleons and nuclei.

DVCS measurements have been the focus of a worldwide effort \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  CERN. The vast majority of the experiments focused on the study of the nucleon's structure. The deuterium was also investigated at HERMES and JLab \cite{Mazouz:2007aa} mainly as a neutron target. Studying the 3D imaging of the nucleon is terms of its fundamental constituents is a very important goal. Understanding how these distributions are modified to provide the binding and structure in a nucleus is as fascinating of a question and an integral part of our quest of using QCD to explore nuclear matter. The study of nuclear DVCS is still in its infancy due to the challenging detection of the low energy recoil nucleus. Until very recently, the HERMES experiment \cite{Ellinghaus:2002zw} was the only one to measure DVCS off heavier nuclei such as $^4$He, N, Ne, Kr and Xe, where only the scattered electron and the real photon are detected. In this paper, we report the first exclusive measurements of DVCS off $^4$He where all products of the reaction are detected including the recoiling $^4$He nucleus.

@@

\begin{figure}[tb]
\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
\vspace{-0.9cm}
\caption{Left: A picture of the \it{eg6} RTPC before insertion into the solenoid. Right: A cross section of the \it{eg6} RTPC perpendicular to the beam direction. An illustration of a $^4$He track originating from the pressurized straw target is shown along with the electrons produced in the drift region.}
\label{fig:RTPC}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\vspace{-0.9cm}
\caption{}
\label{fig:kin-cuts}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\vspace{-0.9cm}
\caption{}
\label{fig:alu}
\end{figure}

@@

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/updated_CFFs.pdf}
\vspace{-0.9cm}
\caption{}
\label{fig:CFF_HA}
\end{figure}

@@

>>>>

\documentclass[nofootinbib,twocolumn,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math

%
\def\Dirac#1{#1\hskip-5pt/}
%
\begin{document}

@@

A wealth of information on the quantum chromodynamics (QCD) structure of 
hadrons lies in the correlations between the momentum and spatial degrees of 
freedom of the fundamental constituent partons, quarks and gluons. Such 
correlations are accessible via the generalized parton distributions (GPDs).  
The GPDs correspond to the coherence between quantum states of different (or 
same) helicity, longitudinal momentum, and transverse position. In an impact 
parameter space, they can be interpreted as a distribution in the transverse 
plane of partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}. A crucial feature of GPDs 
is the access to the transverse position of partons which, combined with their 
longitudinal momentum, leads to the total angular momentum of partons 
\cite{Burkardt:2005hp}. Deep virtual Compton scattering (DVCS) corresponding to 
hard exclusive electroproduction of a real photon, which is considered as the 
cleanest probe to access GPDs and thus study the 3D imaging of nucleons and 
nuclei.

DVCS measurements have been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of the experiments focused on the study of the 
nucleon's structure. The deuterium was also investigated at HERMES and JLab 
\cite{Mazouz:2007aa} mainly as a neutron target. However, studying the 3D 
imaging of the nucleon is a very important goal, understanding how these 
distributions are modified to provide the binding and structure in a nucleus is 
as fascinating of a question and an integral part of our quest of using QCD to 
explore nuclear matter.

A DVCS process on a nuclear target differ from single nucleon scattering in 
providing access to the measure two DVCS channels. In the coherent DVCS 
channel, the target nucleus remains intact and recoils as a whole while 
emitting a real photon ($eA \rightarrow e' A' \gamma$), allowing to measure the 
nuclear GPDs of the target. In the incoherent channel, the nucleus breaks up 
and the DVCS takes place on a bound nucleon that emits the final photon ($eA 
\rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
nucleons and to study the medium modifications of the nucleons in the nuclear 
medium via the GPDs.  Figure \ref{fig:diags} illustrates the dominant mechanism 
for the coherent DVCS channel on $^4$He. At sufficiently large squared electron 
momentum transfer $Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer 
$t$ ($= (p-p')^{2}$), the QCD factorization theorem predicts that the DVCS 
handbag diagram can be factorized into two parts, hard and soft parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and it is calculable through perturbative methods, while the 
soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron.

@@

%introduction
The GPDs are defined for each quark flavor and gluon as matrix
elements of the light cone operators \cite{Belitsky}, describing the transition 
between the initial and final states of a hadron. The GPDs depend on two 
longitudinal momentum fraction variables ($x$, $\xi$) and on the momentum 
transfer $t$ to the target. $x$ is the average longitudinal momentum fraction 
of the parton involved in the process and $\xi$ is the longitudinal fraction of 
the momentum transfer $t$, which is related to the Bjorken variable $x_{B}$: 
$\xi\approx {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$ with
the proton mass $M$ and $\nu=E_e-E_{e^\prime}$. The GPDs $x$ variable cannot be 
measured experimentally in a DVCS reaction. Hence, we measure the GPDs 
convolutions on $x$, the so-called Compton Form Factors (CFF) 
\cite{Guidal:2013rya}.  In a DVCS process, the number of GPDs needed to 
parametrize the partonic structure of a hadron depends on the different 
configurations between the spin of the hadron and the helicity direction of the 
struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
chose the $^4$He nucleus as our target of interest because of it's spinless 
nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
high density and it is a well-known few-body system.

The study of nuclear DVCS is still in its infancy due to the challenging 
detection of the low-energy recoil nuclei in fixed target experiments. Until 
very recently, the HERMES experiment \cite{Ellinghaus:2002zw} was the only one 
to measure DVCS off heavier nuclei such as $^4$He, N, Ne, Kr and Xe, where only 
the scattered electron and the real photon are detected. In this paper, we 
report the first exclusive measurements of coherent DVCS channel off $^4$He 
where all products of the reaction are detected including the recoiling $^4$He 
nucleus. The incoherent DVCS channel measurement from the same data set in in 
preparation and will reported in another publication.

%experimental setup

\begin{figure}[tb]
\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
\vspace{-0.9cm}
\caption{Left: A picture of the CLAS-EG6 RTPC before insertion into the 
   solenoid.  Right: A cross section of the CLAS-EG6 RTPC perpendicular to the 
beam direction. An illustration of a $^4$He track originating from the 
pressurized straw target is shown along with the electrons produced in the 
drift region.}
\label{fig:RTPC}
\end{figure}

%DVCS selection
\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\caption{ The coherent DVCS exclusivity cuts. The black
distributions represent the coherent DVCS events candidate. The shaded
distributions represent the events which passed all the exclusivity cuts
except the quantity plotted. The vertical red lines represent $3\sigma$ cuts.}
\label{fig:kin-cuts}
\end{figure}

%asymmetries 
\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ in
   $Q^{2}$(top panel), $x_{B}$ (middle panel), and $-t$ (bottom panel) bins.  
   The error bars represent the statistical and the systematic uncertainties 
   added quadratically, shown on top in green are error bars representing only 
   the statistical uncertainties. The brown bands represent the systematic
uncertainties, including the normalisation systematic uncertainties. The red
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

@@

%CFF
we extract the GPD $H$ in a model independent way (figure~\ref{fig:CFF}). This 
is possible using the beam-spin asymmetry ($A_{LU}$) expression for spin-zero 
target at leading twist~\cite{BM_2009}:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
%
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. The $\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the nuclear form factor $F_A$ and the independent variables $Q^2$, $x_{B}$ and $t$. These factors are simplified as:
%
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize
%

Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor. Their explicit expressions can be found in .

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/updated_CFFs.pdf}
\vspace{-0.9cm}
\caption{The model-independent extraction of the imaginary (blue points) and
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:CFF_HA}
\end{figure}

%interpretations

%conclusion

%Acknowledgments

@@

\bibitem{Freund_Collins}
A.~Freund and J.C.~Collins, Phys.\ Rev.\ D {\bf 59}, 074009 (1998)

\bibitem{Ji_Osborne}
   X.-D.~Ji and J.~Osborne, Phys.\ Rev.\ D {\bf 58}, 094018 (1998)

\bibitem{Belitsky}
A.~V.~Belitsky and A.~V.~Radyushkin, Phys.\ Rept.\ vol. 418 (2005)

\bibitem{Guidal:2013rya}
 M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
 Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013)

\bibitem{JSeely}
 J. Seely {\it et al.} Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009)
